### 2010-04-02 papers/icfp-2010-desc/paper_idesc.tex
Desc@ICFP: ispell
bonkers substitution remark

Because $\Nat$ is just an inductive type, $\NatD$ is a $\Unit$-indexed
functor. Therefore, the recursive argument is materialised by
$\DVar{\Void}$, where we were using $\DIndx{\!}$ in the previous
presentation. This transformation generalizes to all inductive
types. Moreover, we gain the ability to write mutually recursive
inductive types.

@@

In this section, we have presented the universe of indexed
description. It embraces indexed families of types and, as such,
allows us to write dependent datatypes. Hence, we have presented
several example of indexed datatypes. In this context, we have
presented the free monad construction, together its monadic
operations.

>>>>

Because $\Nat$ is just an inductive type, $\NatD$ is a $\Unit$-indexed
functor. Therefore, the recursive argument is materialised by
$\DVar{\Void}$, where we were using $\DIndx{\!}$ in the previous
presentation. This transformation generalises to all inductive
types. Moreover, we gain the ability to write mutually recursive
inductive types.

@@

The fact that indexed descriptions are closed under substitution
is potentially of considerable utility, if we can exploit this fact:
\[
\idescop{\sigma D}{J}{X} = \idescop{D}{I}{\LAM{i}\idescop{\sigma i}{J}{X}}
\quad \mbox{where}\;\sigma:I\To\IDesc{J}
\]
By observing that a description can be decomposed via substitution, we
split its meaning into a superstructure of substructures, e.g. a
`database containing salaries', ready for traversal operations
preserving the former and targeting the latter.

In this section, we have presented the universe of indexed
description. It embraces indexed families of types and, as such,
allows us to write dependent datatypes. Hence, we have presented
several example of indexed datatypes. In this context, we have
presented the free monad construction, together with its monadic
operations.
